\textbf{Comparing and Analyzing the Effectiveness of Various String Matching Algorithms Across Different Domains}

### 2023-10-23 paper/main.tex
???

\section{References}
\begin{itemize}
	\item [1] eswitha_reddy. (2022, November 7). Applications of string matching algorithms. GeeksforGeeks. https://www.geeksforgeeks.org/applications-of-string-matching-algorithms/ 
	\item [2] Gimel'farb, G. (2011, May 2). String matching algorithms - auckland. String Matching Algorithm. https://www.cs.auckland.ac.nz/courses/compsci369s1c/lectures/GG-notes/CS369-StringAlgs.pdf 
	\item [3] harendrakumar123. (2023, May 8). Introduction to pattern searching - data structure and algorithm tutorial. GeeksforGeeks. https://www.geeksforgeeks.org/introduction-to-pattern-searching-data-structure-and-algorithm-tutorial/ 
	\item [4] Gao, M., Huang, R., Mazumder, A. R., and Li, F. (2022). Comparisons of classic and quantum string matching algorithms*. Proceedings of the 4th International Conference on Advanced Information Science and System. https://doi.org/10.1145/3573834.3574498 
	\item [5] Muhammad Yusuf Muhammad, Mathias Fonkam, Salu George Thandekatu, Sandip Rakshit, and Rao Narasimha Vajjhala. (2023). COMPARATIVE ANALYSIS OF BIT-PARALLEL STRING PATTERN MATCHING ALGORITHMS FOR BIOLOGICAL SEQUENCES. Operational Research in Engineering Sciences: Theory and Applications, 6(1). Retrieved from https://oresta.org/menu-script/index.php/oresta/article/view/554 
	\item [6] Lecroq, T. (2023). Optimal-Hash Exact String Matching Algorithms. arXiv preprint arXiv:2303.05799. 
	\item [7] K Azarudeen et al 2021 J. Phys.: Conf. Ser. 1916 012007 
	\item [8] GeeksforGeeks. (2023c, October 20). Naive algorithm for pattern searching. https://www.geeksforgeeks.org/naive-algorithm-for-pattern-searching/?ref=lbp 
	\item [9] GeeksforGeeks. (2023a, May 4). KMP algorithm for pattern searching. https://www.geeksforgeeks.org/kmp-algorithm-for-pattern-searching/?ref=lbp 
	\item [10] GeeksforGeeks. (2023b, September 6). Rabin-Karp algorithm for pattern searching. https://www.geeksforgeeks.org/rabin-karp-algorithm-for-pattern-searching/?ref=lbp 
\end{itemize}
\end{document}

>>>>

\bibliographystyle{plain}
reference style
\bibliography{references}
\end{document}
